### 2019-02-18 sections/intuition.tex
tasks can be observed

Several observations can be made of a task. The most obvious and basic
observation is determining the value of a task. Not all tasks have a value
though, for example, the empty editor $\Enter \tau$ does not have a value.

We can also observe what potential events a task can take. This is essential in
generating a (graphical) user interface for tasks. For example, the task
$\Edit 5$ can take a new value as input, or it can be cleared, resulting in an
empty editor of type Int.

In order to complete the user interface, we also need to be able to render a
task. This is done in a modular and recursive fashion. Every combinator renders
their sub-tasks in a certain way. For example, when rendering a task that is
composed of a step combinator, we simply render the left side of it.

When we are able to render tasks, and we are able to list all possible inputs,
we can obviously construct a user interface, that displays the current state of
the system, together with buttons that show the potential actions a user can
apply.

Another useful observation is to determine whether a task results in $\Fail$.
This is used by the step combinator, as demonstrated in
Example~\ref{Vending machine}, and the choice combinator, to prevent users from
picking a task that fails.

>>>>

Several observations can be made of tasks.
One of those is determining the value of a task $\Value(t)$.
Not all tasks have a value, for example the empty editor $\Enter \tau$, which makes $\Value$ a partial function.

Another observation is the set of events a task can react to.
This is important for generating user interfaces.
For example, the task $\Edit 5$ can react to value events $v$ and empty events $\Empty$.

In order to render a user interface, the system needs to observe a task's user interface.
This is done compositionally.
User interfaces of combined tasks are composed of the user interfaces of the components.
For example of two tasks combined with a step combinator, only the left hand side is rendered.
Two parallel tasks are rendered next to each other.

In order for the system to actually render a task, it needs to observe the task's value, possible inputs, and user interface.
With this information, the system can then display the current state of the task, together with buttons that show the actions a user can engage in.

The final observation is to determine whether a task results in $\Fail$.
The step combinator and the choice combinator use this to prevent users from picking a failing task.
